---
title: "Statistical models for C-N cycles"
author: "Yunke Peng"
date: "Sep 16, 2020; revision Jan 17 2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---



The analysis below shows four statistical models separately

1. TNPP_model - The logit function of (TNPP_1/GPP) predicted by measured soil C:N, measured age, and observed fAPAR

2. ANPP_model - The logit function of (ANPP_2/GPP) predicted by measured soil C:N,measured age, and observed fAPAR

3. NPPleaf_model - The logit function of (NPP.foliage/ANPP_2) predidicted by PPFD, Tg and vpd

They were all using mixed-effects model. it considered (1|site) as the only random factor. 

The coefficient generated in summary below will be used in next-step: global mapping of C and N cycle.

All using ForC + Sara vicca dataset. For data sources, units, and basic information of input please refer to README in relevant location in Euler.

```{r}
library(lme4)
library(nlme)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)

#For how to collect them. see L1-714 of "/Users/yunpeng/yunkepeng/nimpl_sofun_inputs_final/NPP/Forest_site_orig.R"
NPP_Forest <- read.csv("/Users/yunpeng/data/NPP_final/NPP_Forest.csv")
#aggregate them to apply gwr to get climate input
NPP_Forest1 <- NPP_Forest[,c("lon","lat","z","Begin_year","End_year")]
gwr_sites <- aggregate(NPP_Forest1,by=list(NPP_Forest1$lon,NPP_Forest1$lat,NPP_Forest1$z,NPP_Forest1$Begin_year,NPP_Forest1$End_year), FUN=mean, na.rm=TRUE)
gwr_sites <- gwr_sites[,c("lon","lat","z","Begin_year","End_year")]

#convert before 1980 to 1980-1989
gwr_sites$year_start <- gwr_sites$Begin_year
gwr_sites$year_end <- gwr_sites$End_year
gwr_sites$year_start[gwr_sites$Begin_year<=1980] <- 1980
gwr_sites$year_end[gwr_sites$Begin_year<=1980] <- 1989

summary(gwr_sites)
dim(gwr_sites)

tmn_output <- read.csv("/Users/yunpeng/data/NPP_final/forest_climates_gwr/forest_tmn.csv") #monthly degree celcius
tmx_output <- read.csv("/Users/yunpeng/data/NPP_final/forest_climates_gwr/forest_tmx.csv") #monthly degree celcius
vap_output <- read.csv("/Users/yunpeng/data/NPP_final/forest_climates_gwr/forest_vap.csv")#monthly hPa
pre_output <- read.csv("/Users/yunpeng/data/NPP_final/forest_climates_gwr/forest_pre.csv") #monthly mm/month
radi_output<- read.csv("/Users/yunpeng/data/NPP_final/forest_climates_gwr/forest_radi.csv") #monthly w/m2
alpha_output <- read.csv("/Users/yunpeng/data/NPP_final/forest_climates_gwr/forest_alpha.csv")
lat <- gwr_sites$lat

tmn_site <- tmn_output[,8:247]
tmx_site <- tmx_output[,8:247]
vap_site <- vap_output[,8:247]
pre_site <- pre_output[,8:247]
radi_site <- radi_output[,8:247]
alpha_site <- alpha_output[,8:247]

#just check the data between sites and climates are consistent
summary(tmx_output$lon-gwr_sites$lon)
summary(tmx_output$lat-gwr_sites$lat)
summary(tmx_output$z-gwr_sites$z)
summary(tmx_output$Begin_year-gwr_sites$Begin_year)
summary(tmx_output$End_year-gwr_sites$End_year)

#1. Tg
#solar declination from Jan to Dec
s1 <- (-23.1+ -17.3)/2
s2 <- (-17.3 + -8)/2
s3 <- (-8 + 4.1)/2
s4 <- (4.1 + 14.8)/2
s5 <- (14.8 + 21.9)/2
s6 <- (21.9 + 23.2)/2
s7 <- (23.2 + 18.3)/2
s8 <- (18.3 + 8.6)/2
s9 <-  (8.6 + -2.8)/2
s10 <- (-2.8 + -14.1)/2
s11 <- (-14.1 + -21.6)/2
s12 <- (-21.6 + -23.1)/2

s <- c(s1,s2,s3,s4,s5,s6,s7,s8,s9,s10,s11,s12)
lat <- gwr_sites$lat
xx <- data.frame(matrix(, nrow=nrow(gwr_sites), ncol=240))
output_Tg <- data.frame(matrix(, nrow=nrow(gwr_sites), ncol=240))
#xx = acos(h), h = hour angle of the sun
for (a in 1:12){ 
  month_no <- seq(from = 1, to = 240, by = 12)+a-1
  xx[1:nrow(gwr_sites),month_no]<- -tan(pi*lat/180)*tan(s[a]*pi/180)
}

#check each part of Tg formula
part1 <- (0.5+((1-xx^2)^(0.5))/(2*acos(xx)))[,1:12]
part2 <- (0.5-((1-xx^2)^(0.5))/(2*acos(xx)))[,1:12]
summary(part1)
summary(part2)

#the percentage of tmx was dominated overall
Tg_site <- tmx_site*(0.5+((1-xx^2)^(0.5))/(2*acos(xx)))+ tmn_site*(0.5-((1-xx^2)^(0.5))/(2*acos(xx)))
Tg_site[Tg_site =="NaN"] <- NA
Tg_site[Tg_site < 0] <- NA

vpd_site <- 0.611*exp(17.27*(Tg_site)/((Tg_site)+237.3))-vap_site*0.1 #vap in hPa
vpd_site[vpd_site =="NaN"] <- NA
vpd_site[vpd_site < 0] <- NA

PPFD_site <- radi_site*0.5*4.6 + Tg_site - Tg_site # here + Tg - Tg means it considered growth season
PPFD_site[PPFD_site =="NaN"] <- NA
PPFD_site[PPFD_site < 0] <- NA

alpha_Tg_site <- alpha_site+ Tg_site - Tg_site # here + Tg - Tg means it considered growth season
alpha_Tg_site[alpha_Tg_site >1] <- 1
alpha_Tg_site[alpha_Tg_site < 0] <- NA


#merged now
gwr_sites$alpha_gwr <- rowMeans(alpha_Tg_site,na.rm=TRUE)
gwr_sites$PPFD_gwr <- rowMeans(PPFD_site,na.rm=TRUE)
gwr_sites$Tg_gwr <- rowMeans(Tg_site,na.rm=TRUE)
gwr_sites$vpd_gwr <- rowMeans(vpd_site,na.rm=TRUE)

gwr_sites <- gwr_sites[,!(names(gwr_sites) %in% c("year_start","year_end"))]


NPP_Forest_gwr <- merge(NPP_Forest,gwr_sites,by=c("lon","lat","z","Begin_year","End_year"),all.x=TRUE)
NPP_statistical <- subset(NPP_Forest_gwr,rep_info!="rep" &rep_info!="rep2")

NPP_statistical$age[NPP_statistical$age==999] <- NA
hist(NPP_statistical$age)
hist(NPP_statistical$soilCN)
hist(NPP_statistical$observedfAPAR)

subset(NPP_statistical,GPP<=TNPP_1) # from ForC - might be due to two different sources combined for gpp and npp - ignored it anyways
NPP_statistical$GPP[NPP_statistical$GPP<=NPP_statistical$TNPP_1] <- NA

tnpp_gpp_a <- log((NPP_statistical$TNPP_1/NPP_statistical$GPP)/(1-(NPP_statistical$TNPP_1/NPP_statistical$GPP)))
soilCN_a <- log(NPP_statistical$soilCN)
age_a <- log(NPP_statistical$age)
observedfAPAR_a <- NPP_statistical$observedfAPAR
site_a <- NPP_statistical$site

mod_tnpp <- lmer( tnpp_gpp_a ~ soilCN_a + age_a + observedfAPAR_a  + (1|site_a))
summary(mod_tnpp)
r.squaredGLMM(mod_tnpp)
save(mod_tnpp, file = "/Users/yunpeng/data/NPP_final/statistical_model/mod_tnpp.RData")

library(visreg)
visreg(mod_tnpp,"soilCN_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")
visreg(mod_tnpp,"age_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")
visreg(mod_tnpp,"observedfAPAR_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")


anpp_gpp_b <- log((NPP_statistical$ANPP_2/NPP_statistical$GPP)/(1-(NPP_statistical$ANPP_2/NPP_statistical$GPP)))
mod_anpp <- lmer(anpp_gpp_b ~ soilCN_a + age_a + observedfAPAR_a  + (1|site_a))
summary(mod_anpp)
r.squaredGLMM(mod_anpp)
save(mod_anpp, file = "/Users/yunpeng/data/NPP_final/statistical_model/mod_anpp.RData")

visreg(mod_anpp,"soilCN_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")
visreg(mod_anpp,"age_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")
visreg(mod_anpp,"observedfAPAR_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")



lnpp_data <- subset(NPP_statistical,file=="Sara Vicca"|file=="ForC")
lnpp_anpp_c <- log((lnpp_data$NPP.foliage/lnpp_data$ANPP_2)/(1-(lnpp_data$NPP.foliage/lnpp_data$ANPP_2)))
PPFD_c <- log(lnpp_data$PPFD_gwr)
Tg_c <- lnpp_data$Tg_gwr
vpd_c <- log(lnpp_data$vpd_gwr)
site_c <- lnpp_data$site
mod_lnpp <- lmer(lnpp_anpp_c ~ PPFD_c + Tg_c + vpd_c + (1|site_c))
summary(mod_lnpp)
r.squaredGLMM(mod_lnpp)
save(mod_lnpp, file = "/Users/yunpeng/data/NPP_final/statistical_model/mod_lnpp.RData")

visreg(mod_lnpp,"PPFD_c",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")
visreg(mod_lnpp,"Tg_c",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")
visreg(mod_lnpp,"vpd_c",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")

```

4. Leaf Nmass ~ Vcmax25/LMA (site-species mean), using mixed-effects model based on large dataset from Peng et al. 2021 Communications Biology. it considered (1|site) and (1|species) as the only random factor. 
```{r}
library(lme4)
library(nlme)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)

SP_input <- read.csv(file="/Users/yunpeng/data/leaf_traits/combined_leaf_traits_updated.csv") #new one
summary(SP_input$C_percent)
#mean of value of leaf C = 0.46 or 46%

#remove bahar, as repeated to atkin - and filter a few points with vcmax25<0
SP_input <- subset(SP_input,source!="Bahar et al 2017 New Phytologist")
SP_input <- subset(SP_input,Vcmax25>0)
SP_input$Vcmax.25 <- SP_input$Vcmax25
SP_input$Elevation <- SP_input$z

SP_input2 <- SP_input[,c("lat","lon","Elevation","Vcmax.25","narea","lma")]
sitemean <- aggregate(SP_input2,by=list(SP_input2$lon,SP_input2$lat), FUN=mean, na.rm=TRUE) #site-mean

sitemean$sitename <- paste0("s", 1:nrow(sitemean),sep="") # define sitename (s1,s2..s276)

SP_site1 <- sitemean[,c("lon","lat","sitename")]
SP_final1 <- merge(SP_input,SP_site1,by=c("lat","lon"),all.x=TRUE) #merged sitename to SP data

SP_Vcmax.25 <- aggregate(Vcmax.25~sitename+species,SP_final1,mean) #umol/m2/s
SP_Elevation <- aggregate(Elevation~sitename+species,SP_final1,mean)
SP_narea<- aggregate(narea~sitename+species,SP_final1,mean) # g/m2
SP_lma<- aggregate(lma~sitename+species,SP_final1,mean) # g/m2
SP_lat<- aggregate(lat~sitename+species,SP_final1,mean)
SP_lon<- aggregate(lon~sitename+species,SP_final1,mean)

#merging all observed traits in a site-species dataset.
sitespecies_final <-Reduce(function(x,y) merge(x = x, y = y, by = c("sitename","species"),all.x=TRUE), 
                           list(SP_lon,SP_lat,SP_Elevation,SP_Vcmax.25,
                                SP_narea,SP_lma))

#2. obtain Nrubisco and Nstructural from this large dataset
#firstly, for site-species data
nmass_a <- sitespecies_final$narea/sitespecies_final$lma
vcmax25_lma_a <- sitespecies_final$Vcmax.25/sitespecies_final$lma
sitename_a <- sitespecies_final$sitename
species_a <- sitespecies_final$species

hist(sitespecies_final$narea) # g/m2
hist(sitespecies_final$lma) # g/m2
hist(sitespecies_final$Vcmax.25) # umol/m2/s

library(lme4)

#3. Fit (Nmass) ~ Ns + Nr * (Vcmax25/LMA) - for site-species data
n1 <- lmer(nmass_a~vcmax25_lma_a + (1|sitename_a)+(1|species_a))
summary(n1)
r.squaredGLMM(n1)
save(n1, file = "/Users/yunpeng/data/NPP_final/statistical_model/nmass.RData")

visreg(n1,"vcmax25_lma_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")

```

5. N resorption efficiency ~ Tg + log (vpd) for site-mean.
```{r}
require(data.table)
library(maps)
library(lme4)
library(MuMIn)
library(lmerTest)
library(elevatr)
library(raster)
library(devtools)
devtools::load_all("/Users/yunpeng/yunkepeng/Grassland_new_ingestr_rsofun_20210326/ingestr/")
library(tibble)
library(spgwr)
library(rworldmap)
library(colorRamps)

#2. Input NRE from different sources, rbind, remove repeated data and plot maps, and test a lm model
#Dong is species-based, Du is site-based. To make them consistent, let's use site-based for both df

NRE_Du <- read.csv(file="~/data/NRE_various/NRE_Du/NRE_Du.csv")
NRE_Dong <- read.csv(file="~/data/NRE_various/NRE_Deng/NRE_Deng.csv")

#first - make forest model only
NRE_Du_df <- NRE_Du[,c("lon","lat","NRE","MAT","MAP","VegeType")]
#vegetype =1 is woody ecosystem (all assumed as forest here)
#vegetype = 2 is grassland ecosystem
NRE_Du_df <- subset(NRE_Du_df,VegeType==1)

NRE_Du_df <- aggregate(NRE_Du_df,by=list(NRE_Du_df$lon,NRE_Du_df$lat), FUN=mean, na.rm=TRUE) #site-mean
NRE_Du_df <- NRE_Du_df[,c(3:7)]
head(NRE_Du_df)
dim(NRE_Du_df)

NRE_Dong_df <- NRE_Dong[,c("Longitude","Latitude","NRE.nitrogen.resorption.efficiency.","MAT","MAP","Biome.abbreviation...")]
names(NRE_Dong_df) <- c("lon","lat","NRE","MAT","MAP","biome")
NRE_Dong_df <- subset(NRE_Dong_df,biome=="TRF"|biome=="STF"|biome=="TF"|biome=="BF")
#Forest is TRF,STF,TF,BF
#Desert is Des; Tundra is TUN
#Grassland is Grs
NRE_Dong_df <- aggregate(NRE_Dong_df,by=list(NRE_Dong_df$lon,NRE_Dong_df$lat), FUN=mean, na.rm=TRUE) #site-mean
head(NRE_Dong_df)
NRE_Dong_df <- NRE_Dong_df[,c(3:7)]
dim(NRE_Dong_df)


NRE_Dong_df$source <- "Dong"
NRE_Du_df$source <- "Du"
NRE_df <- rbind(NRE_Du_df,NRE_Dong_df)
summary(NRE_df)

#check repeated data, and remove 4 repeated points from Du et al. paper
NRE_df$repeated <- duplicated(NRE_df[,c("lon","lat")])
subset(NRE_df,repeated==TRUE)
NRE_df <- subset(NRE_df,repeated==FALSE)

#project data
newmap <- getMap(resolution = "low")
plot(newmap, xlim = c(-180, 180), ylim = c(-75, 75), asp = 1)

points(NRE_df$lon,NRE_df$lat, col="red", pch=16,cex=1)

#3. add elevation in this df, based on ingtestr 
siteinfo <- NRE_df[,c("lon","lat")] # present x and y separately
siteinfo$date_start <- lubridate::ymd(paste0(1982, "-01-01"))
siteinfo$date_end <- lubridate::ymd(paste0(2011, "-12-31"))
siteinfo$sitename <- paste0("s", 1:nrow(siteinfo),sep="")
siteinfo <- as_tibble(siteinfo)

df_etopo <- ingest(
  siteinfo,
  source = "etopo1",
  dir = "~/data/etopo/" 
)

NRE_df$elevation <- as.numeric(as.data.frame(df_etopo$data))
subset(NRE_df,elevation<0)
#Some grids > 0, lets' assume -3062 as NA, and others as 0 firstly?
NRE_df$elevation[NRE_df$elevation< -50] <- NA
NRE_df$elevation[NRE_df$elevation< 0] <- 0

#4. Extract site climate/soil/age data (from prediction fields in nimpl simulation) for all NRE sites
#Input data from: ~/data/nimpl_sofun_inputs/map/Final_ncfile
library(rbeni)

#input elevation for global grids
elev_nc <- read_nc_onefile("~/data/watch_wfdei/WFDEI-elevation.nc")
elev <- as.data.frame(nc_to_df(elev_nc, varnam = "elevation"))
head(elev) 

#input nc file
Tg <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/Tg.nc"),
  varnam = "Tg"))

PPFD <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/PPFD.nc"),
  varnam = "PPFD"))

vpd <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/vpd.nc"),
  varnam = "vpd"))

alpha <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/alpha.nc"),
  varnam = "alpha"))

fAPAR <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/fAPAR.nc"),
  varnam = "fAPAR"))

#cbind all predictors, and its lon, lat, z
all_predictors <- cbind(elev,Tg$myvar,PPFD$myvar,vpd$myvar,
                        alpha$myvar,fAPAR$myvar)

names(all_predictors) <- c("lon","lat","z","Tg","PPFD","vpd",
                           "alpha","fAPAR")

Tg_df <- all_predictors[,c("lon","lat","z","Tg")]
PPFD_df <- all_predictors[,c("lon","lat","z","PPFD")]
vpd_df <- all_predictors[,c("lon","lat","z","vpd")]
alpha_df <- all_predictors[,c("lon","lat","z","alpha")]
fAPAR_df <- all_predictors[,c("lon","lat","z","fAPAR")]

#now, apply gwr to extract site predictors' value
head(NRE_df)
NRE_df$elevation[is.na(NRE_df$elevation)==TRUE] <- 0

NRE_site <- NRE_df[,c("lon","lat","elevation")]
names(NRE_site) <- c("lon","lat","z")


a <- 1.5 # which degree (distance) of grid when interpolating gwr from global grids
i <- 1
#Extract Tg, PPFD, vpd, alpha
for (i in c(1:nrow(NRE_site))){ #one site does not have elevation (NA), therefore omitted
  #Tg
  Tg_global <- na.omit(Tg_df)
  NRE_part <- subset(Tg_global,lon>(NRE_site[i,1]-a)&lon<(NRE_site[i,1]+a)&
                       lat>(NRE_site[i,2]-a)&lat<(NRE_site[i,2]+a))
  coordinates(NRE_part) <- c("lon","lat")
  gridded(NRE_part) <- TRUE
  NRE_coord <- NRE_site[i,1:3]
  coordinates(NRE_coord) <- c("lon","lat")
  NRE_site$Tg[i] <- (gwr(Tg ~ z, NRE_part, bandwidth = 1.06, fit.points =NRE_coord,predictions=TRUE))$SDF$pred
  #ppfd
  PPFD_global <- na.omit(PPFD_df)
  NRE_part <- subset(PPFD_global,lon>(NRE_site[i,1]-a)&lon<(NRE_site[i,1]+a)&
                       lat>(NRE_site[i,2]-a)&lat<(NRE_site[i,2]+a))
  coordinates(NRE_part) <- c("lon","lat")
  gridded(NRE_part) <- TRUE
  NRE_coord <- NRE_site[i,1:3]
  coordinates(NRE_coord) <- c("lon","lat")
  NRE_site$PPFD[i] <- (gwr(PPFD ~ z, NRE_part, bandwidth = 1.06, fit.points =NRE_coord,predictions=TRUE))$SDF$pred
  #vpd
  vpd_global <- na.omit(vpd_df)
  NRE_part <- subset(vpd_global,lon>(NRE_site[i,1]-a)&lon<(NRE_site[i,1]+a)&
                       lat>(NRE_site[i,2]-a)&lat<(NRE_site[i,2]+a))
  coordinates(NRE_part) <- c("lon","lat")
  gridded(NRE_part) <- TRUE
  NRE_coord <- NRE_site[i,1:3]
  coordinates(NRE_coord) <- c("lon","lat")
  NRE_site$vpd[i] <- (gwr(vpd ~ z, NRE_part, bandwidth = 1.06, fit.points =NRE_coord,predictions=TRUE))$SDF$pred
  #alpha
  alpha_global <- na.omit(alpha_df)
  NRE_part <- subset(alpha_global,lon>(NRE_site[i,1]-a)&lon<(NRE_site[i,1]+a)&
                       lat>(NRE_site[i,2]-a)&lat<(NRE_site[i,2]+a))
  coordinates(NRE_part) <- c("lon","lat")
  gridded(NRE_part) <- TRUE
  NRE_coord <- NRE_site[i,1:3]
  coordinates(NRE_coord) <- c("lon","lat")
  NRE_site$alpha[i] <- (gwr(alpha ~ z, NRE_part, bandwidth = 1.06, fit.points =NRE_coord,predictions=TRUE))$SDF$pred
}



#combine NRE with site extracted climate and CNrt (Tg, PPFD, vpd, alpha, CNrt)
NRE_climate <- cbind(NRE_df[,c("NRE","MAT","MAP","source")],NRE_site)
summary(NRE_climate)

NRE_climate$vpd[NRE_climate$vpd<=0] <-NA
NRE_climate$nre <- NRE_climate$NRE/100

nre_a <- log(NRE_climate$nre/(1-NRE_climate$nre))
Tg_a <- NRE_climate$Tg
vpd_a <- log(NRE_climate$vpd)

nre_model <- lm(nre_a~Tg_a+vpd_a)
save(nre_model, file = "/Users/yunpeng/data/NPP_final/statistical_model/nre_model_forest.RData")

summary(nre_model)

visreg(nre_model,"Tg_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")

visreg(nre_model,"vpd_a",type="contrast",line=list(col="black",lwd=2), points=list(cex=0.5, pch=16,col="black"),
       ylab=" ",xlab=" ")

####now, grassland
NRE_Du <- read.csv(file="~/data/NRE_various/NRE_Du/NRE_Du.csv")
NRE_Dong <- read.csv(file="~/data/NRE_various/NRE_Deng/NRE_Deng.csv")

#first - make forest model only
NRE_Du_df <- NRE_Du[,c("lon","lat","NRE","MAT","MAP","VegeType")]
#vegetype =1 is woody ecosystem (all assumed as forest here)
#vegetype = 2 is grassland ecosystem
NRE_Du_df <- subset(NRE_Du_df,VegeType==2)
NRE_Du_df <- aggregate(NRE_Du_df,by=list(NRE_Du_df$lon,NRE_Du_df$lat), FUN=mean, na.rm=TRUE) #site-mean
NRE_Du_df <- NRE_Du_df[,c(3:7)]
head(NRE_Du_df)
dim(NRE_Du_df)

NRE_Dong_df <- NRE_Dong[,c("Longitude","Latitude","NRE.nitrogen.resorption.efficiency.","MAT","MAP","Biome.abbreviation...")]
names(NRE_Dong_df) <- c("lon","lat","NRE","MAT","MAP","biome")
NRE_Dong_df <- subset(NRE_Dong_df,biome=="Grs")
#Forest is TRF,STF,TF,BF
#Desert is Des; Tundra is TUN
#Grassland is Grs
NRE_Dong_df <- aggregate(NRE_Dong_df,by=list(NRE_Dong_df$lon,NRE_Dong_df$lat), FUN=mean, na.rm=TRUE) #site-mean
head(NRE_Dong_df)
NRE_Dong_df <- NRE_Dong_df[,c(3:7)]
dim(NRE_Dong_df)

NRE_Dong_df$source <- "Dong"
NRE_Du_df$source <- "Du"
NRE_df <- rbind(NRE_Du_df,NRE_Dong_df)
summary(NRE_df$NRE)
#median of NRE in grassland is 0.69
```