---
title: "Global input for climates (PPFD, Tg, vpd, alpha)"
author: "Yunke Peng"
date: "Nov 18 2020"
output: html_document
---

## Introduction about Global nc files

Elements below are global inputs that will be used in statistical model-based calculations. All data has a final resolution as 0.5 * 0.5 degree - though the resample procedure was needed for soil C/N and LMA. All climate or environmental data (fAPAR, alpha, PPFD, Tg, vpd) has constrained the year from 1980 to 2016 (37 yrs average); while some others (soil C/N, age and LMA) also had a long-term average, according to their paper's description.

 * alpha (SPLASH: asssited by David Sandoval)
 * PPFD (umol/m2/s) (WFDEI: http://www.eu-watch.org/gfx_content/documents/README-WFDEI%20(v2016).pdf)
 * Tg (degree celcius) (CRU ts 4.01: https://crudata.uea.ac.uk/cru/data/hrg/cru_ts_4.01/)
 * vpd (kPa) (CRU ts 4.01: https://crudata.uea.ac.uk/cru/data/hrg/cru_ts_4.01/)

The process below will provide original codes of soil C/N, stand age, fAPAR, alpha and LMA, as well as description text of PPFD, Tg, vpd. Vcmax25 will be seperately processed in SOFUN in Euler then.

#1. PPFD (description and main calculation were provided)
PPFD is instantaneous photosynthetic photon flux density (umol/m2/s). We used the 30 yrs average data (1982-2011), which was originally derived from time-integrated (24 hrs) daily Shortwave radiation (SWdown) from WFDEI. In order to convert from SWdown to PPFD, we need to calculate them as:

PPFD (umol/m2/s) = SWdown (w/m2) * 4.6 * 0.5 

where Solar radiation was converted to incident PPFD assuming a flux : energy ratio of 4.6 umol/J and a photosynthetically active fraction of 0.50 (Peng et al. 2020; New Phytologist).

The code below will represent the global map of final output:

#2. Tg (description and main calculation were provided)
Tg is growth temperature (degree celcius). We used the 30 yrs average data (1982-2011), which was originally derived from monthly maximum temperature (Tmx) and minimum temperature (Tmn) from CRU ts 4.01. See formula below:

The solar declination used were average value from each two month's starting day
https://www.cambridge.org/core/services/aop-cambridge-core/content/view/212421E8457A41C47B64D809BDEF53CA/9780511845727apx7_p351-352_CBO.pdf/solar_geometry_and_radiation_approximations.pdf

#3. vpd (description and main calculation were provided)
vpd is vapor-pressure-deficient (kPa). We used the 30 yrs average data (1982-2011), which was originally derived from monthly data from CRU ts 4.01. See formula below (Peng et al. 2020 New Phytologist):

vpd <- 0.611*exp(17.27*(Tg)/((Tg)+237.3))-vap*0.1 

where Tg (in celcius degree) was derived from above, and vap (hPa) was derived from CRU ts 4.01 monthly data. The code below shows the global map of final output.

The original Rdata was based on code /Users/yunpeng/yunkepeng/nimpl_sofun_inputs_final/climates_30yrs_monthly/climates_WFDEI_CRU.R

```{r}
load(file = "/Users/yunpeng/yunkepeng/nimpl_sofun_inputs_final/climates_30yrs_monthly/WFDEI_CRU_1980_2016.Rdata")
devtools::load_all("/Users/yunpeng/yunkepeng/rbeni/")
library(dplyr)
library(raster)
library(ncdf4)
library(dplyr)
library(maps)
library(rgdal)

#calculate growth temperature
total_month <- (2016-1980+1) * 12

#solar declination from Jan to Dec: https://www.cambridge.org/core/services/aop-cambridge-core/content/view/212421E8457A41C47B64D809BDEF53CA/9780511845727apx7_p351-352_CBO.pdf/solar_geometry_and_radiation_approximations.pdf
s1 <- (-23.1+ -17.3)/2
s2 <- (-17.3 + -8)/2
s3 <- (-8 + 4.1)/2
s4 <- (4.1 + 14.8)/2
s5 <- (14.8 + 21.9)/2
s6 <- (21.9 + 23.2)/2
s7 <- (23.2 + 18.3)/2
s8 <- (18.3 + 8.6)/2
s9 <-  (8.6 + -2.8)/2
s10 <- (-2.8 + -14.1)/2
s11 <- (-14.1 + -21.6)/2
s12 <- (-21.6 + -23.1)/2

s <- c(s1,s2,s3,s4,s5,s6,s7,s8,s9,s10,s11,s12)

lat <- monthly_tmn[,2]
xx <- data.frame(matrix(, nrow=259200, ncol=total_month))
output_Tg <- data.frame(matrix(, nrow=259200, ncol=total_month))

for (a in 1:12){ 
  month_no <- seq(from = 1, to = total_month, by = 12)+a-1
  xx[1:259200,month_no]<- -tan(pi*lat/180)*tan(s[a]*pi/180)
}

#check each part of Tg formula
part1 <- (0.5+((1-xx^2)^(0.5))/(2*acos(xx)))[,1:12]
part2 <- (0.5-((1-xx^2)^(0.5))/(2*acos(xx)))[,1:12]
summary(part1)
summary(part2)
#the percentage of tmx was dominated overall

output_Tg<-monthly_tmx[,3:(total_month+2)]*(0.5+((1-xx^2)^(0.5))/(2*acos(xx)))+ monthly_tmn[,3:(total_month+2)]*(0.5-((1-xx^2)^(0.5))/(2*acos(xx)))
output_Tg[output_Tg =="NaN"] <- NA
output_Tg[output_Tg < 0] <- NA

output_vpd <- 0.611*exp(17.27*(output_Tg)/((output_Tg)+237.3))-monthly_vap[,3:(total_month+2)]*0.1 #vap in hPa
output_vpd[output_vpd =="NaN"] <- NA
output_vpd[output_vpd < 0] <- NA

output_PPFD <- monthly_radi[,3:(total_month+2)]*0.5*4.6 +output_Tg - output_Tg # here + Tg - Tg means it considered 
output_PPFD[output_PPFD =="NaN"] <- NA

#now, all done. Primarily calculated each year's average - then avaerage of years. Calculate na.rm=TRUE average.
Tg <- data.frame(matrix(, nrow=259200, ncol=12))
vpd <- data.frame(matrix(, nrow=259200, ncol=12))
PPFD <- data.frame(matrix(, nrow=259200, ncol=12))

#firstly calculate based on years (37 years to one year) - then calculate monthly average of one year
for (a in 1:12){ 
  month_no <- seq(from = 1, to = total_month, by = 12)+a-1
  Tg[1:259200,a]<- rowMeans(output_Tg[,month_no],na.rm = TRUE)
  vpd[1:259200,a]<- rowMeans(output_vpd[,month_no],na.rm = TRUE)
  PPFD[1:259200,a]<- rowMeans(output_PPFD[,month_no],na.rm = TRUE)
}

Tg <- rowMeans(Tg,na.rm = TRUE)
vpd <- rowMeans(vpd,na.rm = TRUE)
PPFD <- rowMeans(PPFD,na.rm = TRUE)

lonlat <- monthly_tmn[,1:2]

Tg_final <- cbind(lonlat,Tg)
names(Tg_final) <- c("lon","lat","Tg")
Tg_final$Tg[Tg_final$Tg=="NaN"] <- NA
Tg_df_output <- Tg_final

vpd_final <- cbind(lonlat,vpd)
names(vpd_final) <- c("lon","lat","vpd")
vpd_final$vpd[vpd_final$vpd=="NaN"] <- NA
vpd_df_output <- vpd_final

PPFD_final <- cbind(lonlat,PPFD)
names(PPFD_final) <- c("lon","lat","PPFD")
PPFD_final$PPFD[PPFD_final$PPFD=="NaN"] <- NA
PPFD_df_output <- PPFD_final

#prepare lon and lat
library(ncdf4)
ncin <- nc_open("~/data/watch_wfdei/WFDEI-elevation.nc")
lon <- ncvar_get(ncin,"lon")
lat<-ncvar_get(ncin,"lat")

#output PPFD nc file - In Euler its path is same: "~/data/nimpl_sofun_inputs/map/Final_ncfile"
PPFD_nc <- list(df_to_grid(PPFD_df_output,varnam = "PPFD", lonnam = "lon", latnam = "lat"))
names(PPFD_nc) <- "PPFD"
varams = "PPFD"
test <- list(lon,lat,PPFD_nc,varams)
names(test) <- c("lon","lat","vars","varams")
write_nc2(test,varnams = "PPFD",long_name = "PPFD",units = "umol/m2/s",
          path = "~/data/nimpl_sofun_inputs/map/Final_ncfile/PPFD.nc")

#output Tg nc file - In Euler its path is same: "~/data/nimpl_sofun_inputs/map/Final_ncfile"
Tg_nc <- list(df_to_grid(Tg_df_output,varnam = "Tg", lonnam = "lon", latnam = "lat"))
names(Tg_nc) <- "Tg"
varams = "Tg"
test <- list(lon,lat,Tg_nc,varams)
names(test) <- c("lon","lat","vars","varams")
write_nc2(test,varnams = "Tg",long_name = "Growth temperature",units = "Degree Celcius",
          path = "~/data/nimpl_sofun_inputs/map/Final_ncfile/Tg.nc")

#output vpd nc file - In Euler its path is same: "~/data/nimpl_sofun_inputs/map/Final_ncfile"
vpd_nc <- list(df_to_grid(vpd_df_output,varnam = "vpd", lonnam = "lon", latnam = "lat"))
names(vpd_nc) <- "vpd"
varams = "vpd"
test <- list(lon,lat,vpd_nc,varams)
names(test) <- c("lon","lat","vars","varams")
write_nc2(test,varnams = "vpd",long_name = "vapor prssure deficient",units = "KPa",
          path = "~/data/nimpl_sofun_inputs/map/Final_ncfile/vpd.nc")



library(raster)

coordinates(PPFD_final) <- ~lon+lat 
gridded(PPFD_final) <- TRUE
r3 <- raster(PPFD_final, "PPFD") 
plot(r3)

coordinates(Tg_final) <- ~lon+lat 
gridded(Tg_final) <- TRUE
r3 <- raster(Tg_final, "Tg") 
plot(r3)

coordinates(vpd_final) <- ~lon+lat 
gridded(vpd_final) <- TRUE
r3 <- raster(vpd_final, "vpd") 
plot(r3)

``` 

#4. alpha

```{r}
library(raster)
library(ncdf4)
library(dplyr)
library(maps)
library(rgdal)
alphalist <- list.files(path = "~/data/alpha/data_orig/",full.names = T) # here this file includes 116 data - that is the annual alpha from 1901 to 2016

#alphalist <- list.files(path = "E:/C-N cycling/Carbon allocation/672 sites analysis/alpha/",full.names = T)

#Input alpha from a list of data frame from 1901 to 2016 (list 116)
empty_alpha <- data.frame(matrix(NA)) 

#calculate alpha within 37 years (1980-2016)
alphalist[80]
alphalist[116]
for (i in 80:116){ #here 82:111 means 1980-2016
  load(file = alphalist[i])
  empty_alpha[1:259200,i-79] <- rowMeans(SP_result_monthly,na.rm = TRUE)
}

final_alpha <- rowMeans(empty_alpha,na.rm = TRUE)

alpha_input <- as.data.frame(cbind(lonlat,final_alpha)) 
names(alpha_input) <- c("lon","lat","alpha")

df_alpha <- alpha_input

coordinates(alpha_input) <- ~lon+lat 
gridded(alpha_input) <- TRUE

r4 <- raster(alpha_input, "alpha") 
plot(r4)

#output nc file - In Euler its path is same: "~/data/nimpl_sofun_inputs/map/Final_ncfile"
df_alpha$alpha[df_alpha$alpha == "NaN"] <- NA
summary(df_alpha)

alpha_nc <- list(df_to_grid(df_alpha,varnam = "alpha", lonnam = "lon", latnam = "lat"))
names(alpha_nc) <- "alpha"
varams = "alpha"
test <- list(lon,lat,alpha_nc,varams)
names(test) <- c("lon","lat","vars","varams")
write_nc2(test,varnams = "alpha",long_name = "alpha",units = "unitless",
          path = "~/data/nimpl_sofun_inputs/map/Final_ncfile/alpha.nc")

``` 
