---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

---
title: "A demo for uncertainty of npp"
author: "Yunke Peng"
date: "Dec 20 2020"
output: html_document
---


## Here is the demo for calculating uncertainty of npp


1. library
```{r}
rm(list=ls())
library(tidyverse)  # depends
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)

```

2. Just input 30 nc files of 30 years gpp --> and caluclate them as an average
```{r}

#### Forest
#1. In our path (with multiple years data), identify which is the first year and end year of those files
firstyr_data <- 1982 # In data file, which is the first year
endyr_data <- 2011 # In data file, which is the last year
location <- "/Users/yunpeng/data/output/latest_forest/"
alloutput_list <- list.files(location,full.names = T)

#input elevation nc file, which will be cbind with global df directly
elev_nc <- read_nc_onefile("~/data/watch_wfdei/WFDEI-elevation.nc")
#elev_nc <- read_nc_onefile("D:/PhD/nimpl_sofun_inputs/Data/Elevation/WFDEI-elevation.nc")
elev <- as.data.frame(nc_to_df(elev_nc, varnam = "elevation"))

#2. Create a function to specify path, loop many years nc file and output a dataframe (lon, lat, var).
inputnc <- function(name,start_year,end_year){
  #-----------------------------------------------------------------------
  # Input: 
  # name: gpp, npp, anpp, vcmax25, leafcn, nuptake...
  # start_year: e.g. 1981
  # end_year: e.g. 2016
  # location: e.g "D:/PhD/nimpl_sofun_inputs/Data/output/" or in Euler: "~/yunkebranch_units/outputnc/"
  #-----------------------------------------------------------------------
  output_allyears <- data.frame(matrix(NA))
  # first, include all years annual data into a daframe
  for (i in firstyr_data:endyr_data){
    if (name == "npp"){
      nc <- read_nc_onefile(alloutput_list[grepl("a.npp.nc", list.files(location,full.names = T))][i-firstyr_data+1]) #we only rely this to filter npp.nc file...
    } else {
      nc <- read_nc_onefile(alloutput_list[grepl(name, list.files(location,full.names = T))][i-firstyr_data+1]) #Input nc
    }
    output_year <- nc_to_df(nc, varnam = name)[,3] #Yearly output
    output_allyears[1:259200,i-firstyr_data+1] <- output_year #here first column represents first year of data file 's output
  }
  names(output_allyears) <- paste(name,firstyr_data:endyr_data,sep="")
  #this variable above (output_allyears), could be end of the function, which is variable at multiple years. But for our purporses, we need mean of select years
  #then, only calculate means of selected years
  output_selected_yrs <- rowMeans(output_allyears[,(start_year-firstyr_data+1):(end_year-firstyr_data+1)],na.rm = TRUE) # only calculated means based on selected start and end year (see function)
  coord <- nc_to_df(nc, varnam = name)[,1:2] # obtain lon and lat
  final_output <- cbind(coord,elev[,3],output_selected_yrs) # combine lon, lat,z with rowmeans variable
  names(final_output) <- c("lon","lat","z",name)
  return(final_output)
  #-----------------------------------------------------------------------
  # Output: output_final: the output data (259200 * 3) including lon, lat and value
  #-----------------------------------------------------------------------
}

#3. select data over 30 years, each df includes lon, lat, z, var
gpp_df <- inputnc("gpp",1982,2011)
```

3. Calculate npp - based on prediction fields from fitted regressions
```{r}

Tg <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/Tg.nc"),
  varnam = "Tg"))

PPFD <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/PPFD.nc"),
  varnam = "PPFD"))

vpd <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/vpd.nc"),
  varnam = "vpd"))

fAPAR <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/fAPAR.nc"),
  varnam = "fAPAR"))

age <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/age.nc"),
  varnam = "age"))

CNrt <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/CNrt.nc"),
  varnam = "CNrt"))

LMA <- as.data.frame(nc_to_df(read_nc_onefile(
  "~/data/nimpl_sofun_inputs/map/Final_ncfile/LMA.nc"),
  varnam = "LMA"))

load("/Users/yunpeng/data/NPP_final/statistical_model/mod_tnpp.RData")
summary(mod_tnpp)

#four fitted coefficients
a1 <- summary(mod_tnpp)$coef[1,1]
a2 <- summary(mod_tnpp)$coef[2,1]
a3 <- summary(mod_tnpp)$coef[3,1]
a4 <- summary(mod_tnpp)$coef[4,1]

npp_grid <- gpp_df$gpp * (1/(1 + exp(-(a1 + a2 * log(CNrt$myvar)+ a3*log(age$myvar)+a4* fAPAR$myvar))))

gpp_npp_grid <- as.data.frame(cbind(gpp_df,npp_grid))
dim(gpp_npp_grid)
names(gpp_npp_grid) <- c("lon","lat","z","gpp","npp")
summary(gpp_npp_grid)

#just plot
plot_map3(gpp_npp_grid[,c("lon","lat","gpp")], 
                varnam = "gpp",plot_title = "gpp(gC/m2/yr)",
                latmin = -65, latmax = 85)

plot_map3(gpp_npp_grid[,c("lon","lat","npp")], 
                varnam = "npp",plot_title = "npp (gC/m2/yr)",
                latmin = -65, latmax = 85)

```

4. Calculate uncertainty of npp/gpp. The step was based on three steps
- since we know logit (npp/gpp) = regression. We assumed npp/gpp =a, and regression =b. Then a = 1 / (1 + exp(-b)).

- the uncertainty of b (delta b) can be calculated directly based on summary(mod_tnpp)$sigma, as loaded in above.

```{r}

mod_tnpp_uncertainty <- summary(mod_tnpp)$sigma  #random factor: a population parameter - estimated automatically
#mod_tnpp_uncertainty <- sd(residuals(mod_tnpp))  #random factor: a parameter in a subset of the population - estimated manually
mod_tnpp_uncertainty
```

- The uncertainty of a (i.e. NPP/GPP), was equal to delta b * (deriative a / deriative b). After adjustment, a = delta b *exp(-b)/((1 + exp(-b))^2). Where b is the outputted map from regression calculations.

```{r}
#firstly, calculate b (see text in 3)
tnpp_b <- a1 + a2 * log(CNrt[,3])  +
  a3*log(age[,3]) + a4 * fAPAR[,3]

#secondly, uncertainty of a (npp/gpp) (see text in 3)

npp_gpp_uncertainty <- mod_tnpp_uncertainty *  exp(-tnpp_b) / ( (1 + exp(-tnpp_b)) ^2)

gpp_npp_grid$npp_gpp_uncertainty <- npp_gpp_uncertainty

plot_map3(gpp_npp_grid[,c("lon","lat","npp_gpp_uncertainty")], 
                varnam = "npp_gpp_uncertainty",plot_title = "Uncertainty of npp/gpp",
                latmin = -65, latmax = 85)

```

5. Finally calculate uncertainty of npp. Since npp = (npp/gpp) * gpp --> delta npp =  npp * sqrt((delta(npp/gpp)/(npp/gpp))^2 + (delta(gpp)/gpp)^2).
- Within delta(gpp)/gpp --> delta gpp was obtained from standard deviations between predicted and measured gpp in FLUXNET sites (Stocker et al. 2021 GMD); and gpp was accordinly defined as mean values of site-predicted gpp values.

```{r}
#firstly, calculate uncertainty of gpp, and mean values of predicted gpp

load("/Users/yunpeng/data/gpp_gmd/stocker20gmd_outputs/rdata_objects/out_eval_FULL.Rdata")
#Data in Euler is from: /cluster/work/climate/bestocke/data/stocker20gmd_outputs/rdata_objects/out_eval_FULL.Rdata 

obs <-out_eval_FULL$gpp$fluxnet$data$meandf$obs
pred <- out_eval_FULL$gpp$fluxnet$data$meandf$mod
obs_pred <- as.data.frame(cbind(obs,pred))
obs_pred <- na.omit(obs_pred)

# According to textbook:Uncertainty estimates obtained as standard deviations of repeated measurement results are called A type uncertainty estimates. 
# In this way,  “sample mean” corresponds to the true GPP, and the “observation” is the modelled GPP.
obs_pred$variance <- (obs_pred$obs - obs_pred$pred)^2
uncertainty_gpp <- sqrt(sum(obs_pred$variance)/nrow(obs_pred))
uncertainty_gpp

mean_gpp <- mean(obs_pred$pred,na.rm=TRUE)
mean_gpp

#calculate uncertainty of npp
gpp_npp_grid$uncertainty_npp <- gpp_npp_grid$npp * sqrt((npp_gpp_uncertainty/(gpp_npp_grid$npp/gpp_npp_grid$gpp))^2 + 
                                       (uncertainty_gpp/mean_gpp)^2)
# the range was reasonalbly within npp, 
summary(gpp_npp_grid$uncertainty_npp/gpp_npp_grid$npp)

```

(5) Therefore, the uncertainty map of npp was obtained.

```{r}

plot_map3(gpp_npp_grid[,c("lon","lat","uncertainty_npp")], 
                varnam = "uncertainty_npp",plot_title = "Uncertainty of npp (gC/m2/yr)",
                latmin = -65, latmax = 85)

```
